Verifying Demonstrations

### 2019-02-05 paper/protocol.tex
Changes commas to semi-colons in enumeration
Removes wrongful paragraph break

%\section{\CROCUS:\@ A protocol for crowd counting estimation}%
\section{The \CROCUS Protocol}
\label{Protocol}

We now present \CROCUS, a protocol for privately verifiable crowd counts.
The protocol consists of three phases:
before the protest, with the setup and registration steps (\cref{ProtocolSetup}),
during the protest, with the creation, join, participation, and submission steps (\cref{ProtocolDuring})
and after the protest, with the verification step (in
\cref{ProtocolVerification}). Note that some of the figures with
protocol minutae from related work are in the
appendix.

Several entities are involved in our protocol.
First, a \emph{certificate authority} (\ac{CA}) is responsible for certifying a one-to-one mapping between a 
person's identity and a cryptographic key\footnote{%
  This can be done by a centralized authority, such as a nation state with, 
  \eg, passports; or a decentralized authority, as in the case of a a 
  collective authority~\cite{collective-signing} powered by 
  proof-of-personhood~\cite{proof-of-personhood}.
}.
The \ac{CA} is only involved in the setup phase.
Second, a participant is an individual who wants to participate in a given 
protest.
A participant can assume three different roles:
\begin{enumerate}
\item The \emph{organizer} has written a manifesto for the protest and forwards it to others.
\item A \emph{protester} is attending the protest and asks witnesses to vouch 
  for their presence.
\item A \emph{witness} provides proofs to protesters which state that the 
  protester was indeed participating, constructed such that the proofs are verifiable by 
  third parties.
\end{enumerate}
In general, there is one organizer and every participant can act as
either or both protester and witness.

\subsection{Pre-protest phase}%
\label{ProtocolSetup}

The setup step is only run once and is the same as in Anon-Pass~\cite{AnonPass}.
More precisely, we have simply adapted their description to our notation, but otherwise kept the setting as similar as possible.

\emph{Setup: \((\spk, \ssk)\gets \CROCUSsetup\).}

During the setup phase, the \ac{CA} creates all the needed keys.
The \ac{CA} generates a service public-private key-pair \((\spk, \ssk)\gets 
  \ACsetup\) (see \cref{ACsignAlg}).

\emph{Registration: \(\sk\gets 
    \Proto{\CROCUSreg[_P][\spk]}{\CROCUSreg[_{\CA}][\ssk]}\).}
During the registration step, each participant generates a secret key and 
obtains a signature on it by the \ac{CA} but without revealing it to the 
\ac{CA}.
At the end, each participant will have a signed secret key while the \ac{CA} 
will issue only one signature per participant but without knowing the 
association between a particular key and the identity of the participant.
The participant chooses \(k, r\rgets \ZZ_q\) uniformly randomly and runs 
\(\sigma \gets \Proto{\ACgetSig[\spk, k, r]}{\ACissueSig[\spk, \ssk]}\) (see 
\cref{ACacAlg}).
Upon success, the participant sets \(\sk = (\sigma, k, r)\).

The setup and registration steps can be done once and the keys can be reused 
for an arbitrary number of protests.
Thus, the registration step could be easily integrated as part of the issuance 
of national identity cards, passports or \acp{eID}.

\subsection{Protest phase}%
\label{ProtocolDuring}

%The join, participation and submission phases are as follows.
% illustrated in \cref{fig:ProtocolOverview}.

The participation proof share constructed in the
participation phase is illustrated in \cref{fig:ProofFig}.

@@

\emph{Creation of a protest: the manifesto.}
The organizer writes a manifesto for the protest, which describes its cause.
This manifesto could take the form of any intelligible text.
The organizer will then distribute this manifesto to people through
any suitable means  (\eg on the Web, on placards, \etc).
If they agree with the cause, they will use the knowledge of the
manifesto to join the protest.

\emph{Joining as a protester: \((\pid, t_s)\gets 
    \CROCUSjoin[_P][\text{manifesto}]\).}
A protester who wants to join the protest will use the manifesto to
compute an identifier for the cause by hashing the manifesto,
\(\cid\gets \Hash[\mfst]\) (and comparing the result to that received
from the organizer, we omit this in the protocol for readibility).
Afterwards, this identifier is used to create the protest-specific identifier 
for the protester, \(\pid\gets \ACprf[_{\sk_P}][\cid]\) (see 
\cref{fig:ProofFig} and \cref{ACprfAlg}).
The protester should also receive a time-correlated random value from the 
time-stamping service, \(t_s\gets \TSget\).

@@

\emph{Participation: \(\pi\gets
    \Proto{\CROCUSparticipate[\cid, \sk_P]}{\CROCUSwitness[\sk_W, \spk]}\),}
In the participation phase, the protester and 
the witness construct the proof share of the protester (\cref{fig:ProofFig}).

The protester sends \(\pid\) to the witness.
Then they run the protocol \(\Proto{\ACproveSig[\spk, k, r, 
    \sigma]}{\ACverifySig[\spk, \ssk]}\) (see \cref{ACacAlg}).
Note that the \ac{PK} in \cref{ACacAlg} must be run as \iac{PPK}.
If the protocol succeeds, the witness will compute \(\wid \gets 
  \ACprf[_{\sk_W}][\pid]\) and send \((\wid, t_s', l)\) to the protester.

\emph{Submission: \(\psh_P\gets \CROCUSsubmit[_P][\cid, \pid, \wid, t_s, t_s',  l]\).}
The protester should as soon as possible commit the proof-share data to the 
time-stamping service and receive the proof of commitment, \(t_e\gets 
  \TSstamp[\Hash[\cid, \pid, \wid, t_s, t_s', l]]\).
The remaining operations are not time critical.

@@

\emph{Submission: \(\psh_W\gets \CROCUSsubmit[_W][\cid, \pid, \wid, t_s, t_s', 
    l]\).}
The witness should, just as the protester, commit the proof-share data to the 
time-stamping service, \(t_e'\gets \TSstamp[\Hash[\cid, \pid, \wid, t_s, t_s', 
  l]]\).
(This is to make the time interval as early as possible, whoever is the faster 
will submit it.)
Then, without any time requirements, the witness computes \iac{NIZK} proof 
\(\corr_{\wid}\) as follows:
\begin{multline*}
  \corr_{\wid}\gets \SPK\left\{ (\sk_W) : \right. \\
    \begin{aligned}
      \wid &= \ACprf[_{\sk_W}][\pid] \quad \land \\
      \sigma_W' &= \left. \ACblind[\ACsign[_{\ssk}][\sk_W]] \right\}
    \end{aligned} \\
      (\cid, \pid, \wid, t_s, t_s', l).
\end{multline*}
Finally, the witness uploads the tuple \[
  \psh_W = (\cid, \pid, \wid, t_s, t_s', t_e', l, \corr_{\wid})
\] for permanent storage.

Here is an overview of the protocol.

%\begin{figure}
% \centering
  \small
 % \begin{minipage}{\linewidth}
    \begin{align*}
      O\to \text{all}\colon & \text{manifesto} \\
      P\colon & t_s\gets \TSget \\
        & \cid\gets \Hash[\text{manifesto}], \\
        & \pid\gets \ACprf[_{\sk_P}][\cid] \\
      W\colon & t_s'\gets \TSget
      \\[-1em]
      \noalign{\hfill Join}
      \midrule
      \noalign{\hfill Participation}
      \\[-3em]
      P\to W\colon & \pid \\
      P\leftrightarrow W\colon &
        \PPK\mleft\{ (\sk_P) : \mright. \\
        & \qquad \pid = \ACprf[_{\sk_P}][\cid], \\
        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{\ssk}][\sk_P]] \mright\} 
        \\
      W\colon & \wid\gets \ACprf[_{\sk_W}][\pid] \\
      W\to P\colon & (\wid, t_s', l)
      \\[-1em]
      \noalign{\hfill Participation}
      \midrule
      \noalign{\hfill Submission}
      \\[-2em]
      P\colon & t_e\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]] \\
      W\colon & t_e'\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]] \\
      W\to S\colon & (\cid, \pid, \wid, t_s, t_s', t_e, l, \pi_{\wid}),\quad 
      \text{where} \\
        & \pi_{\wid} = \SPK\mleft\{ (\sk_W) : \mright. \\
        & \qquad \wid = \ACprf[_{\sk_W}][\pid], \\
        & \qquad \mleft. \sigma_W' = \ACblind[\ACsign[_{\ssk}][\sk_W]]\mright\} 
        \\
        & \qquad\qquad (\cid, \pid, \wid, t_s, t_s', l) \\
      P\to S\colon & (\cid, \pid, \wid, t_s, t_s', t_e, l, \pi_{\pid}),\quad 
      \text{where}\\
        & \pi_{\pid} = \SPK\mleft\{ (\sk_P) : \mright. \\
        & \qquad \pid = \ACprf[_{\sk_P}][\cid], \\
        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{\ssk}][\sk_P]] \mright\} 
        \\
        & \qquad\qquad (\cid, \pid, \wid, t_s, t_s', l)
    \end{align*}
%  \end{minipage}
%  \caption{%
%     An overview of the Join, Participation and Submission phases of \CROCUS.\@
%     The organizer \(O\) broadcasts the manifesto.
%     The protester \(P\), witness \(W\) and their computations are as in \cref{fig:ProofFig}.
%     Finally, both \(P\) and \(W\) submit the proof shares to a
%     permanent storage \(S\). Note that \pid always refers to the
%     protester whose presence is being witnessed.
%   }%
%   \label{fig:ProtocolOverview}
% \end{figure}
\normalsize

\subsection{Post-protest phase}%
\label{ProtocolVerification}

% While there are various ways for verifying the participation count, hereafter, 
% we will detail the two suggested just after \cref{DefParticipationCount}.
% In the first approach, we do not trust individual witnesses, rather we \emph{assume} that it is difficult for Alice to find more than \(\theta\) witnesses willing to collude.
% Thus, the strength comes from the number of witnesses and we require at least \(\theta\) witnesses to accept a participation proof as valid.
% In the second approach, we trust specific witnesses, but no others.
% In this case, to accept a participation proof as valid, we require at least one trusted witness, the independent journalist Jane.
% It is the strength function \(\str\) of \cref{DefParticipationCount} that 
% differ in the two cases.
% We will first give the procedure and then how to construct the two different 
% strength functions.

To verify the participation count for a protest \(\prtst\) with identifier \(cid_0\),
a verifier must download from the storage system S the set \(S_{\prtst}\) of all \(s_P\) and \(s_W\) tuples containing \(cid_0\).
Then from \(S_{\prtst}\), a verifier can build, in succession,
(a) the valid proof shares \(s_j^{(i)}\) for all matching pairs \((s_P,s_W)\) corresponding to a witness  \(i\) and a protester \(j\),
(b) the participation proof \(\prf_{j}\) for each protester \(j\),
(c) the set \(\prfs_{\prtst}^{\str,\theta}\) of eligible participation proofs for all protesters in \(P\),
 and finally the participation count, cardinality of the previous set.

More precisely, given: \\
\(S_{\prtst} = \{ (cid, pid, wid, l, t_s, t_s', t_c, \corr) \in \pshs \mid \cid = \cid_0 \} \) \\
and a matching pair \((s_P, s_W) \in {S_{\prtst}}^2\) for a witness \(i\) and a protester \(j\)
with \(s_P = (cid_0, pid_j, wid_i, l, t_s, t_s', t_c, \psi_i)\)
and  \(s_W = (cid_0, pid_j, wid_i, l, t_s, t_s', t_c', \psi_j)\),
%, with matching values for \(cid_0, pid_j, wid_i, l, t_s, t_s'\),
the verifier can build a valid proof share \(s_j^{(i)}\) certified by  \(i\) for \(j\) as follow:
verify \(\psi_i\) and \(\psi_j\),
let \(t = [max(t_s, t_s'), min(t_c, t_c')]\),
let \(s_j^{(i)} = (cid_0, pid_j, wid_i, l, t)\), as in \cref{DefProofShare},
check that \(s_j^{(i)}\) is valid (i.e. happened during and at the location of the protest), as in \cref{DefProofShare}.

Then the set of all valid proof shares for a protester \(j\) constitutes its participation proof \(\pi_{j}\), as in \cref{DefParticipationProof},
and the verifier thus can derive the set of \((\str,\theta)\)-eligible participation proofs \(\prfs_{\prtst}^{\str,\theta}\) for all protesters for the protest \(\prtst)\), as in \cref{DefParticipationProof}.
Finally, the  participation count \(|\prfs_{\prtst}^{\str,\theta}|\) is the cardinality of this set by the same \cref{DefParticipationProof}.

% MOST PROBABLY obsolete below v

%To verify the participation count for a protest \(\prtst\)  with identifier $\cid$
%(see \cref{DefProtest}), a verifier must download all the proof shares \[
%  \psh_i =   (\cid, \pid_j, \wid_i, t_s^{(i)}, t_s^{\prime (i)}, t_e^{(i)}, 
%  t_e^{\prime   (i)}, l_i, \corr_{\pid_j}^{(i)}, \corr_{\wid_i})
%\] for each protester \(j\) from the ledger, verify \(\corr_{\pid_j}^{(i)}\), 
%\(\corr_{\wid_i}\) and that the interval \(\interval{\max(t_s^{(i)}, 
%    t_s^{\prime (i)})}{\min(t_e^{(i)}, t_e^{\prime (i)})}\subseteq t\) and that 
%\(l_i\subseteq  l\).
%Any proof share that does not verify correctly will be discarded.
%At this point, the verifier has constructed the set \(S\) from 
%\cref{DefProofShares} and can thus construct any participation proof 
%\(\prf_{\pid_j, P}\) as in \cref{DefParticipationProof}.
%Now the verifier can compute the participation count \(|\prfs_P^{\str, 
%    \theta}|\) as in \cref{DefParticipationCount}.

%__________________________

% In the case \emph{without} trusted witnesses, all the weights equal to 1 is equivalent to counting the elements in the set, 
% \(\str[\prf_{\pid_j, P}] = |\prf_{\pid_j, P}|\).

In the case of trusted witnesses, each such trusted witness must
publish or otherwise inform the 
verifier of which proof shares she has signed, \eg by giving a list 
of all such proof shares or digitally signing each proof share\footnote{
 To achieve witness privacy in this situation, one could employ a group or 
 ring signature scheme for all trusted witnesses.
 Then one learns that at least one trusted witness must have been there.
}.

Note that anyone who does the counting can choose the eligibility
criteria (time interval, location, number of regular or trusted
witnesses, who is considered to be a trusted witness) for their count
and as long as these are published along with the result, anyone can
verify the correctness under those criteria.

% Then the verifier can define \[
%   \str[\prf_{\pid_j, P}] = \begin{cases}
%     1 & \text{if \(\exists \psh_i\in \prf_{\pid_j, P}\) that is such a proof 
%       share} \\
%     0 & \text{otherwise}
%   \end{cases}
% \] and sets \(\theta = 1\).

>>>>

\section{\CROCUS:\@ A protocol for crowd counting estimation}%
\label{Protocol}

We now present \CROCUS, a protocol for privately verifyiable crowd counts.
The protocol consists of five phases: setup (in \cref{ProtocolSetup}),
join, participation, submission (all in in \cref{ProtocolDuring}) and
verification (in \cref{ProtocolVerification}).

Several entities are involved in our protocol.
First, \iac{CA} is responsible for certifying a one-to-one mapping between a 
person's identity and a cryptographic key\footnote{%
  This can be done by a centralized authority, such as a nation state with, 
  \eg, passports; or a decentralized authority, as in the case of a a 
  collective authority~\cite{collective-signing} powered by 
  proof-of-personhood~\cite{proof-of-personhood}.
}.
The \ac{CA} is only involved in the setup phase.
Second, a participant is an individual who wants to participate in a given 
protest.
A participant can assume three different roles:
\begin{enumerate}
\item The \emph{organizer} has written a manifesto for the protest and forward it to others.
\item A \emph{protester} is attending the protest and asks witnesses to vouch 
  for his presence.
\item A \emph{witness} provides proofs to protesters which state that the 
  protester was indeed participating and such that the proofs are verifiable by 
  third parties.
\end{enumerate}
In general, there is one organizer and every participant can act alternatively 
as both protester and witness.

\subsection{Setup phase}%
\label{ProtocolSetup}

The setup phase is only run once and is the same as in Anon-Pass~\cite{AnonPass}.
More precisely, we have simply adapted their description to our notation, but otherwise we have the setting as similar as possible.

\emph{Setup: \((\spk, \ssk)\gets \CROCUSsetup\).}
During the setup phase, the \ac{CA} creates all the needed keys.
The \ac{CA} generates a service public-private key-pair \((\spk, \ssk)\gets 
  \ACsetup\) (see \cref{ACsignAlg}).

\emph{Registration: \(\sk\gets 
    \Proto{\CROCUSreg[_P][\spk]}{\CROCUSreg[_{\CA}][\ssk]}\).}
During the registration phase, each participant generates a secret key and 
obtains a signature on it by the \ac{CA} but without revealing it to the 
\ac{CA}.
At the end, each participant will have a signed secret key while the \ac{CA} 
will issue only one signature per participant but without knowing the 
association between a particular key and the identity of the participant.
The participant chooses \(k, r\rgets \ZZ_q\) uniformly randomly and runs 
\(\sigma \gets \Proto{\ACgetSig[\spk, k, r]}{\ACissueSig[\spk, \ssk]}\) (see 
\cref{ACacAlg}).
Upon success, the participant sets \(\sk = (\sigma, k, r)\).

The setup and registration phases can be done once and the keys can be reused 
for an arbitrary number of protests.
Thus, the registration phase could be easily integrated as part of the issuance 
of national identity cards, passports or \acp{eID}.

\subsection{Creation, join and participation in a protest and submission of proofs}%
\label{ProtocolDuring}

The join, participation and submission phases are illustrated in \cref{fig:ProtocolOverview}.
The participation proof share that will be constructed in the participation phase is illustrated in \cref{fig:ProofFig}.

\emph{Creation of a protest: the manifesto.}
The organizer will write a manifesto for the protest, which describes its cause.
This manifesto could take the form of any intelligible text.
The organizer will then distribute this manifesto to people through any means he wants (\eg on the Web, on placards, \etc).
If they agree on the cause, they will use the knowledge of the manifesto to join the protest.

\emph{Joining as a protester: \((\pid, t_s)\gets 
    \CROCUSjoin[_P][\text{manifesto}]\).}
A protester who wants to join the protest will use the manifesto to compute an identifier for the cause by hashing the manifesto, \(\cid\gets \Hash[\mfst]\).
Afterwards, this identifier is used to create the protest-specific identifier 
for the protester, \(\pid\gets \ACprf[_{\sk_P}][\cid]\) (see 
\cref{fig:ProofFig,fig:ProtocolOverview} and \cref{ACprfAlg}).
The protester should also receive a time-correlated random value from the 
time-stamping service, \(t_s\gets \TSget\).

@@

\begin{figure}
  \centering
  \small
  \begin{minipage}{\linewidth}
    \begin{align*}
      O\to \text{all}\colon & \text{manifesto} \\
      P\colon & t_s\gets \TSget \\
        & \cid\gets \Hash[\text{manifesto}], \\
        & \pid\gets \ACprf[_{\sk_P}][\cid] \\
      W\colon & t_s'\gets \TSget
      \\[-1em]
      \noalign{\hfill Join}
      \midrule
      \noalign{\hfill Participation}
      \\[-3em]
      P\to W\colon & \pid \\
      P\leftrightarrow W\colon &
        \PPK\mleft\{ (\sk_P) : \mright. \\
        & \qquad \pid = \ACprf[_{\sk_P}][\cid], \\
        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{\ssk}][\sk_P]] \mright\} 
        \\
      W\colon & \wid\gets \ACprf[_{\sk_W}][\pid] \\
      W\to P\colon & (\wid, t_s', l)
      \\[-1em]
      \noalign{\hfill Participation}
      \midrule
      \noalign{\hfill Submission}
      \\[-2em]
      P\colon & t_e\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]] \\
      W\colon & t_e'\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]] \\
      W\to S\colon & (\cid, \pid, \wid, t_s, t_s', t_e, l, \pi_{\wid}),\quad 
      \text{where} \\
        & \pi_{\wid} = \SPK\mleft\{ (\sk_W) : \mright. \\
        & \qquad \wid = \ACprf[_{\sk_W}][\pid], \\
        & \qquad \mleft. \sigma_W' = \ACblind[\ACsign[_{\ssk}][\sk_W]]\mright\} 
        \\
        & \qquad\qquad (\cid, \pid, \wid, t_s, t_s', l) \\
      P\to S\colon & (\cid, \pid, \wid, t_s, t_s', t_e, l, \pi_{\pid}),\quad 
      \text{where}\\
        & \pi_{\pid} = \SPK\mleft\{ (\sk_P) : \mright. \\
        & \qquad \pid = \ACprf[_{\sk_P}][\cid], \\
        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{\ssk}][\sk_P]] \mright\} 
        \\
        & \qquad\qquad (\cid, \pid, \wid, t_s, t_s', l)
    \end{align*}
  \end{minipage}
  \caption{%
    An overview of the Join, Participation and Submission phases of \CROCUS.\@
    The organizer \(O\) broadcasts the manifesto.
    The protester \(P\), witness \(W\) and their computations are as in \cref{fig:ProofFig}.
    Finally, both \(P\) and \(W\) submit the proof shares to a
    permanent storage \(S\). Note that \pid always refers to the
    protester whose presence is being witnessed.
  }%
  \label{fig:ProtocolOverview}
\end{figure}

@@

\emph{Participation: \(\pi\gets
    \Proto{\CROCUSparticipate[\cid, \sk_P]}{\CROCUSwitness[\sk_W, \spk]}\),}
In the participation phase (see \cref{fig:ProtocolOverview}), the protester and 
the witness construct the proof share of the protester (\cref{fig:ProofFig}).

The protester sends \(\pid\) to the witness.
Then they run the protocol \[
  \Proto{\ACproveSig[\spk, k, r, \sigma]}{\ACverifySig[\spk, \ssk]}
\] (see \cref{ACacAlg}).
Note that the \ac{PK} in \cref{ACacAlg} must be run as \iac{PPK}.
If the protocol succeeds, the witness will compute \(\wid \gets 
  \ACprf[_{\sk_W}][\pid]\) and send \((\wid, t_s', l)\) to the protester.

\emph{Submission: \(\psh_P\gets \CROCUSsubmit[_P][\cid, \pid, \wid, t_s, t_s',  l]\).}
The participant should as soon as possible commit the proof-share data to the 
time-stamping service and receive the proof of commitment, \(t_e\gets 
  \TSstamp[\Hash[\cid, \pid, \wid, t_s, t_s', l]]\).
The remaining operations are not time critical.

@@

\emph{Submission: \(\psh_W\gets \CROCUSsubmit[_W][\cid, \pid, \wid, t_s, t_s', 
    l]\).}
The witness should, just as the participant, commit the proof-share data to the 
time-stamping service, \(t_e'\gets \TSstamp[\Hash[\cid, \pid, \wid, t_s, t_s', 
  l]]\).
(This is to make the time interval as early as possible, whoever is the faster 
will submit it.)
Then, without any time requirements, the witness computes \iac{NIZK} proof 
\(\corr_{\wid}\) as follows:
\begin{multline*}
  \corr_{\wid}\gets \SPK\left\{ (\sk_W) : \right. \\
    \begin{aligned}
      \wid &= \ACprf[_{\sk_W}][\pid] \quad \land \\
      \sigma_W' &= \left. \ACblind[\ACsign[_{\ssk}][\sk_W]] \right\}
    \end{aligned} \\
      (\cid, \pid, \wid, t_s, t_s', l).
\end{multline*}
Finally, the witness uploads the tuple \[
  \psh_W = (\cid, \pid, \wid, t_s, t_s', t_e', l, \corr_{\wid})
\] for permanent storage.

\subsection{Verifying the participation count}%
\label{ProtocolVerification}

While there are various ways for verifying the participation count, hereafter, 
we will detail the two suggested just after \cref{DefParticipationCount}.
In the first approach, we do not trust individual witnesses, rather we \emph{assume} that it is difficult for Alice to find more than \(\theta\) witnesses willing to collude.
Thus, the strength comes from the number of witnesses and we require at least \(\theta\) witnesses to accept a participation proof as valid.
In the second approach, we trust specific witnesses, but no others.
In this case, to accept a participation proof as valid, we require at least one trusted witness, the independent journalist Jane.
It is the strength function \(\str\) of \cref{DefParticipationCount} that 
differ in the two cases.
We will first give the procedure and then how to construct the two different 
strength functions.

To verify the participation count for a subprotest \(\sprtst = (\cid, t, l)\) 
(see \cref{DefProtest}), a verifier must download all the proof shares \[
  \psh_i =   (\cid, \pid_j, \wid_i, t_s^{(i)}, t_s^{\prime (i)}, t_e^{(i)}, 
  t_e^{\prime   (i)}, l_i, \corr_{\pid_j}^{(i)}, \corr_{\wid_i})
\] for each protester \(j\) from the ledger, verify \(\corr_{\pid_j}^{(i)}\), 
\(\corr_{\wid_i}\) and that the interval \(\interval{\max(t_s^{(i)}, 
    t_s^{\prime (i)})}{\min(t_e^{(i)}, t_e^{\prime (i)})}\subseteq t\) and that 
\(l_i\subseteq  l\).
Any proof share that does not verify correctly will be discarded.
At this point, the verifier has constructed the set \(S\) from 
\cref{DefProofShares} and can thus construct any participation proof 
\(\prf_{\pid_j, P}\) as in \cref{DefParticipationProof}.
Now the verifier can compute the participation count \(|\prfs_P^{\str, 
    \theta}|\) as in \cref{DefParticipationCount}.

In the case \emph{without} trusted witnesses, all the weights equal to 1 is equivalent to counting the elements in the set, 
\(\str[\prf_{\pid_j, P}] = |\prf_{\pid_j, P}|\).

In the case \emph{with} trusted witnesses, each trusted witness must inform the 
verifier of which proof shares that he or she has signed, \eg by giving a list 
of all such proof shares or digitally sign each proof share\footnote{%
  To achieve witness privacy in this situation, one could employ a group or 
  ring signature scheme for all trusted witnesses.
  Then one learns that at least one trusted witness must have been there.
}.
Then the verifier can define \[
  \str[\prf_{\pid_j, P}] = \begin{cases}
    1 & \text{if \(\exists \psh_i\in \prf_{\pid_j, P}\) that is such a proof 
      share} \\
    0 & \text{otherwise}
  \end{cases}
\] and sets \(\theta = 1\).

### 2019-02-05 paper/system-model.tex

To set the stage, we will now describe our system model including
assumptions and a summary of the desired properties for crowd
counting% and the adversary model
.

@@

% \subsection{Adversary model}%
% \label{adversary-model}

% We consider two types of adversaries: 
% \begin{enumerate*} 
% \item an \emph{honest-but-curious adversary} of up to national scale representing a government that can observe any
% messages sent on communication links (\ie either during the protest or later during the upload of the participation), and 
% \item a \emph{malicious adversary} that can control a minority of equipments such as participants' or witnesses' smartphones or servers used for the ledger such as miners for a blockchain. 
% \end{enumerate*}

>>>>

To set the stage, we will now describe our system model including assumptions, a summary of the desired properties for crowd counting and the adversary model.

@@

\subsection{Adversary model}%
\label{adversary-model}

We consider two types of adversaries: 
\begin{enumerate*} 
\item an \emph{honest-but-curious adversary} of up to national scale representing a government that can observe any
messages sent on communication links (\ie either during the protest or later during the upload of the participation), and 
\item a \emph{malicious adversary} that can control a minority of equipments such as participants' or witnesses' smartphones or servers used for the ledger such as miners for a blockchain. 
\end{enumerate*}

### 2019-02-05 paper/timestamp.tex

\subsection{Time-stamping and storage: ledger}%
\label{StorageProperties}\label{timestamp}\label{ledger}

We need a robust time-stamping service, \(\TS\), which implements the \(\TSget\), \(\TSstamp\) and \(\TStime\) requests such that
\simon{"request" feels weird to me. Are we sure that's the right word?}
\begin{itemize}
  \item \(\rho \gets \TSget\) yields a value \(\rho\) at time \(t\), \(\rho\) is difficult to guess before time \(t\) and \(\TStime[\rho] = t\);
  \item \(\pi\gets \TSstamp[x]\) yields a value \(\pi\) at time \(t\) such that \(\TSverify[x, \pi]\to \top\) and \(\TStime[\pi] = t\).
\end{itemize}

@@

The tuple \((\rho_{t_0}, m, \pi_{t_1})\) can be used to prove that \(m\) was created within the time interval \(\interval{t_0}{t_1}\).
The verifier computes \(h'\gets \Hash[m, \rho_{t_0}]\) and checks whether \(\TSverify[h', \pi_{t_1}] = \top \land \TStime[\rho_{t_0}] > t_0\land 
  \TStime[\pi_{t_1}] < t_1\).

\(\TS\) can be instantiated by an open-membership distributed ledger (\eg a blockchain) such as Bitcoin~\cite{Bitcoin}, secured via Proof-of-Work consensus, or OmniLedger~\cite{OmniLedger}, secured via Byzantine consensus.
If a blockchain is used for \(\TS\), the \(\TSstamp[x]\) request includes \(x\) in the blockchain and returns the identifier of the block into which \(x\) was included.
The \(\TSget\) request returns the hash of the most recent block of the chain (\ie the head).
\footnote{In situations where forks are common, it is relatively easy to adapt this process to look at a few blocks before the head and avoid the issue of the stamp becoming invalid later.}
The returned hash is difficult to predict since it depends on the content of the block, populated by other users and by the creator of the block with additional randomness (\eg nonces and secrets).

Regarding consensus resilience, it is advisable to use a blockchain with a high number of participants even if it means sharing the blockchain with other services.
The resilience of the Byzantine consensus relies on honest participants outnumbering malicious participants.
A similar reasoning can be made with Proof-of-Work consensus in which the computing power of the honest participants must be greater than the one of malicious participants.
In both cases, assuming a majority of honest members in the population, the more participants the merrier.

We require a few additional properties from \(\TS\) that are already provided by blockchains.
First, \(\TS\) must be continuously extended, such as in Bitcoin in which blocks are created every 10 minutes on average.
Second, \(\TS\) must provide \emph{immutability} and availability to any data committed through \(\TSstamp\) to ensure verifiability of the data by anyone at any time.
Note that thanks to \(\TS\) immutability, once a user has committed their data, that user only need to store some confirmation value instead of the data itself.
For instance, in the case of a blockchain, it would be sufficient for a user to only store both the hash of the block containing their participation proof and the hash of the proof.

>>>>

\subsection{Time-stamping and storage --- distributed ledger}%
\label{StorageProperties}\label{timestamp}\label{ledger}

We need a robust time-stamping service, \(\TS\), which implements the \(\TSget\), \(\TSstamp\) and \(\TStime\) requests such that
\begin{itemize}
  \item \(\rho \gets \TSget\) yields a value \(\rho\) at time \(t\), \(\rho\) is difficult to guess before time \(t\) and \(\TStime[\rho] = t\);
  \item \(\pi\gets \TSstamp[x]\) yields a value \(\pi\) at time \(t\) such that \(\TSverify[x, \pi]\to \top\) and \(\TStime[\pi] = t\).
\end{itemize}

@@

The tuple \((\rho_{t_0}, m, \pi_{t_1})\) can be used to prove that \(m\) was created within the time interval \(\interval{t_0}{t_1}\).
The verifier computes \(h'\gets \Hash[m, \rho_{t_0}]\) and checks whether 
\(\TSverify[h', \pi_{t_1}] = \top\) and \(\TStime[\rho_{t_0}] \geq t_0\land 
  \TStime[\pi_{t_1}] \leq t_1\).

\(\TS\) can be instantiated by an open-membership distributed ledger (\eg a blockchain) such as Bitcoin~\cite{Bitcoin}, secured via Proof-of-Work consensus, or OmniLedger~\cite{OmniLedger}, secured via Byzantine consensus.
If a blockchain is used for \(\TS\), the \(\TSstamp[x]\) request includes \(x\) in the blockchain and returns the identifier of the block into which \(x\) was included.
The \(\TSget\) request returns the hash of the most recent block of the chain 
(\ie the head).%
\footnote{In situations where forks are common, it is relatively easy to adapt this process to look at a few blocks before the head and avoid the issue of the stamp becoming invalid later.}
The returned hash is difficult to predict since it depends on the content of 
the block, populated by other users and by the creator of the block with 
additional randomness (\eg nonces and secrets).

Regarding consensus resilience, it is advisable to use a blockchain with a high 
number of participants and preferably sharing the blockchain with other 
services.
The resilience of the Byzantine consensus relies on honest participants outnumbering malicious participants.
A similar reasoning can be made with Proof-of-Work consensus in which the computing power of the honest participants must be greater than the one of malicious participants.
In both cases, assuming a majority of honest members in the population, the more participants the merrier.
We want to share the blockchain with other services due to privacy (and 
anti-censorship) reasons, analogous to the idea of \enquote{domain fronting}.

We require a few additional properties from \(\TS\) that are already provided by blockchains.
First, \(\TS\) must be continuously extended, such as in Bitcoin in which blocks are created every 10 minutes on average.
Second, \(\TS\) must provide \emph{immutability} and availability to any data committed through \(\TSstamp\) to ensure verifiability of the data by anyone at any time.
Once the data from a user is committed, the user can choose to only store some confirmation value instead of the data itself.
In the case of a blockchain, it would be sufficient for a user to only store both the hash of the block containing her participation proof and the hash of the proof.
